How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-08 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

The ANZCTR was established in 2005 as part of a coordinated global effort to improve research quality and transparency in clinical trials reporting. Researchers responsible for overseeing a clinical trial are expected to register full details before commencing participant enrolment. Details required for registration follow a standardised template (reference or supp file), which covers important details about participant eligibility, intervention(s) being evaluated, study design and outcomes. As part of study design, researchers are required to provide a summary of statistical methods and planned analyses. 
<!---Upon successful registration, the trial is assigned a unique registration number for use in future reporting in scientific publications. --->
All trials registered on ANZCTR are publicly available and can be searched for via an online portal.

All studies on ANZCTR were downloaded on 1~February~2020 in XML format. Studies were excluded if the statistical methods section was empty or labelled as "Not applicable", "Nil" or "None".

@@

>>>>

The ANZCTR was established in 2005 as part of a coordinated global effort to improve research quality and transparency in clinical trials reporting. Researchers responsible for overseeing a clinical trial are expected to register full details before commencing participant enrolment. Details required for registration follow a standardised template (reference or supp file), which covers important details about participant eligibility, intervention(s) being evaluated, study design and outcomes. As part of study design, researchers are required to provide a "brief description" of the sample size calculations, statistical methods and planned analyses [@ANZCTR]. 
<!---Upon successful registration, the trial is assigned a unique registration number for use in future reporting in scientific publications. --->
All trials registered on ANZCTR are publicly available and can be searched for via an online portal.

All studies available on ANZCTR were downloaded on 1 February 2020 in XML format. Studies were excluded if the statistical methods section was empty or labelled as "Not applicable", "Nil" or "None".

@@

There were 28,008 downloaded studies, and 9,632 (34\%) had a statistical methods section.
